Thesis Title

### 2022-03-08 chapters/introduction.tex
Updates from Overleaf

De novo assembly refers to the bioinformatics process whereby reads are assembled into a draft genome using only the sequence information of the reads.

@@

\paragraph{Overlap, Layout Consensusus assembly} \label{sssec:OLC_assembly} \mbox{}\\

>>>>

De novo assembly refers to the bioinformatics process whereby reads are assembled into a draft genome using only the sequence information of the reads. Two methods are used to obtain draft genomes without the need of a reference genome: (1) through Overlap, Layout and Consensus, or (2) De Bruijn graph assembly (see Figure \ref{fig:figure6}).

@@

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{figures/introduction/Figure 6.png}
\caption{\textbf{Approaches to \textit{de novo} genome assemble.} BLABLA. Adapted from \cite{ayling_new_2020}}.
\label{fig:figure6}
\end{figure*}

\paragraph{Overlap, Layout and Consensus assembly} \label{sssec:OLC_assembly} \mbox{}\\
